### 2019-11-21 thesis.tex
another appendix (maybe)

Collisional interactions are the central point of the present thesis.
However, the formalism presented in \Cref{noneigenmode}, departs from
the weak turbulence equations, which are the nonlinear approximation of
the kinetic equations for low-amplitude instabilities in a collisionless
plasma. The contribution of the correlations between \emph{source}
fluctuations, that account for collisional interactions  (see.~\cite{
  klimon,Tigik2015}), are then retrieved by the inclusion of noneigenmode
contribution in both wave and particle kinetic equations. The difference
of this new approach is that

@@

>>>>

Collisional interactions are the central point of the present thesis.
However, the formalism presented in \Cref{noneigenmode}, departs from the
weak turbulence equations, which are the nonlinear approximation of the
kinetic equations for low-amplitude instabilities in a collisionless plasma.
The contribution of the correlations between \emph{source} fluctuations,
which account for collisional interactions  (see.~\cite{klimon,Tigik2015}),
are then retrieved with the inclusion of noneigenmode contribution.
in both wave and particle kinetic equations. The difference
of this new approach is that

@@

\chapter{Klimontovich formalism}
\label{app-klimo}
% The Klimontovich formalism is the basis of 
% This appendix has the objective to complement important concepts discussed in
% \Cref{noneigenmode}. 
% In this appendix I present the standard approach that leads to the well known
% Balescu-Lenard collision integral. The objective here is to put the formalism
% presented in this thesis in a context where it can be compared with the usual
% text-book method that employs the Klimontovich statistical formulation. The
% derivation shown here is basically a version of Chapter 4

\section{Micorscopic equations for a fully ionized plasma}
\label{mic-eq}
Let us consider a fully ionized hydrogen plasma, where $e_a$ and $m_a$ are,
respectively the charge and the mass of the particles of species $a$, that
can be or electrons $e_e\equiv -e$ or protons (ions) $e_i\equiv e$. Denoting
$N_a$ as the total number of particles of species $a$ in the plasma, the
neutrality condition of a plasma is given by
\begin{equation}
  \sum_ae_aN_a=0.  
\end{equation}

The probability distribution function for a N-body system in phase-space,
$x\equiv({\bf r, v})$, is given by the Klimontovich function
\begin{equation}
N_a(x,t)=N_a({\bf r, v}, t)=\sum_{i=1}^{N_a}
\delta[{\bf r}-{\bf r}_{ia}(t)]
\delta[{\bf v}-{\bf v}_{ia}(t)].
\end{equation}
